Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-27 paper.tex
update

\subsubsection{Single-step Transition}
Before go into describing how the machine evaluates expressions, we firstly define several helper functions.
As we mentioned in section \ref{anfsyntax}, the atomic expressions are either a variable, or
a literal @lambda@ term. So the helper function @atomicEval@ handles these two
cases and evaluates atomic expressions to closures in a straightforward way.
The @alloc@ function generates a fresh address, and always allocates an unique integer under the domain
of store.
The @isAtomic@ function is used as a predicate of whether the expression is atomic.

@@

The first case is that the control of current state is a @Let@ expression,
and its right-hand side is an function application.
By calling function @atomicEval@, we obtain the closure that callee @f@ stands for.
The successor state's control then transfers to the @body@ expression of closure,
with an updated environment and an update store. The new environment is extended
from closure's environment and mapped @v@ to a fresh address @addr@.
The new store is extended with @addr@ mapping to the value of @ae@,
which is evaluated from @atomicEval@.
In the meanwhile, a new frame @frame@ is pushed onto the stack @k@.
This @frame@ contains the variable name @x@ at left-hand side position of @Let@,
the body expression of @Let@, and the lexical environment of the body expression.

@@

\textbf{Abstracting Definitional Interpreters.}

On the other side, with the insight from Reynold's seminal paper 
\emph{Definitional interpreters for higher-order programming languages} \cite{reynolds1972definitional}
that the defined language will inherit properties
from the defining language, \citeauthor{darais2017abstracting} construct abstracting 
definitional interpreters that automatically inherit the pushdown control-flow 
property from its defining language.

@@

We start from the AAM with unbounded stack.

@@

@@

simply trun evaluation contexts into higher-order continuations

\subsubsection{Computable Refunctionalization}

>>>>

\subsubsection{Single-step Transition}
Before go into describing how the machine evaluates expressions, we firstly define several helper functions.
As we mentioned in section \ref{anfsyntax}, the atomic expressions are either a variable, or
a literal @lambda@ term. So the atomic expression evaluator @atomicEval@ handles these two
cases and evaluates atomic expressions to closures in a straightforward way.
The @alloc@ function generates a fresh address, and always allocates an unique integer under the domain
of store.
The @isAtomic@ function is used as a predicate of whether the expression is atomic.

@@

The first case is that the control of current state is a @Let@ expression,
and its right-hand side is an function application.
By calling evaluator @atomicEval@, we obtain the closure that callee @f@ stands for.
The successor state's control then transfers to the @body@ expression of closure,
with an updated environment and an update store. The new environment is extended
from closure's environment and mapped @v@ to a fresh address @addr@.
The new store is extended with @addr@ mapping to the value of @ae@,
which is evaluated from @atomicEval@.
In the meanwhile, a new frame @frame@ is pushed onto the stack @k@.
This @frame@ contains the variable name @x@ at left-hand side position of @Let@,
the body expression of @Let@, and the lexical environment of the body expression.

@@

\textbf{Abstracting Definitional Interpreters.}
On the other side, with the insight from Reynold's seminal paper 
\emph{Definitional interpreters for higher-order programming languages} \cite{reynolds1972definitional}
that the defined language will inherit properties
from the defining language, \citeauthor{darais2017abstracting} construct abstracting 
definitional interpreters that automatically inherit the pushdown control-flow 
property from its defining language.

@@

We start from the AAM with unbounded stack.
In fact, since later we will eliminate the call stack and transform to
higher-order continuations, it does not matter what kind of AAM we start from.

@@

simply trun evaluation contexts into higher-order continuations.
We establish pushdown control-flow, but this is not computable.

@@

\subsubsection{Caching Fixed-Points}
